---
title: "challenge3"
author: "fblome"
date: "29 11 2020"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Challenge 3 - Data wrangling

## 1. Libraries
````{r eval=FALSE}
# Tidyverse
library(tidyverse)
library(vroom)

# Data Table
library(data.table)

````

## 2. Data Import
````{r eval = FALSE}
# 2.1 Assignee  Data ----
col_types_ass <- list(
  id = col_character(),
  type = col_integer(),
  name_first = col_skip(NULL),
  name_last = col_skip(NULL),
  organization = col_character()
)

assignee_tbl <- vroom(
  file       = "00_data/patents_data/assignee.tsv", 
  delim      = "\t", 
  col_types  = col_types_ass,
  na         = c("", "NA", "NULL")
)


#2.2 Patents assignee data ----

col_types_pat_ass <- list(
  patent_id = col_character(),
  assignee_id = col_character(),
  location_id = col_skip()
)

patent_assignee_tbl <- vroom(
  file        = "00_data/patents_data/patent_assignee.tsv",
  delim       = "\t",
  col_types   = col_types_pat_ass,
  na          = c("", "NA", "NULL")
)

#2.3 Patents data ----

col_types_pat <- list(
  id = col_character(),
  type = col_character(),
  number = col_skip(),
  country = col_skip(),
  date = col_date("%Y-%m-%d"),
  abstract = col_skip(),
  title = col_skip(),
  kind = col_skip(),
  num_claims = col_skip(),
  filename = col_skip(),
  withdrawn = col_skip()
)

patents_tbl <- vroom(
  file        = "00_data/patents_data/patent.tsv",
  delim       = "\t",
  col_types   = col_types_pat,
  na          = c("", "NA", "NULL")
)


# 2.4 USPC data ----

col_types_uspc <- list(
  uuid = col_skip(),
  patent_id = col_character(),
  mainclass_id = col_character(),
  subclass_id = col_skip(),
  sequence = col_skip()
)

uspc_tbl <- vroom(
  file        = "00_data/patents_data/uspc.tsv",
  delim       = "\t",
  col_types   = col_types_uspc,
  na          = c("", "NA", "NULL")
)

````

## 3. Merge data
````{r eval = FALSE}
# Convert to data.table ----

setDT(assignee_tbl)
setDT(patent_assignee_tbl)
setDT(patents_tbl)
setDT(uspc_tbl)

#Merge assignee and patent_assignee by assignee_id
combined_assignee_data <- merge(x = assignee_tbl, y = patent_assignee_tbl,
                                by.x    = "id",
                                by.y    = "assignee_id", 
                                all.x = FALSE,
                                all.y = TRUE)

# Merge combined_assignee_data with patents_tbl
combined_patent_data <- merge(x = combined_assignee_data, y = patents_tbl,
                              by.x      = "patent_id",
                              by.y      = "id",
                              all.x = FALSE,
                              all.y = TRUE)

# Merge combined_patent_data with uspc_tbl
combined_uspc_data <- merge(x = combined_patent_data, y = uspc_tbl,
                            by.x        = "patent_id",
                            by.y        = "patent_id",
                            all.x = FALSE,
                            all.y = TRUE)


````

## 4. Analysis of Data

## 4.1 What US company / corporation has the most patents?
List the 10 US companies with the most assigned/granted patents.
Calculation
````{r eval=FALSE}
most_patents_US <- combined_assignee_data[type == 2, .N, by = organization] # 2- US company or Corporation
most_patents_US[order(-N)]  %>% # order in descending way and slice only first 10 entries
    slice(1:10) %>%
  write_rds("02_data_wrangling/most_patents_US.rds")
````
Result
````{r}
most_patents_US <- read_rds("patents_data/most_patents_US.rds")
most_patents_US
````

## 4.2 What US company had the most patents granted in 2019?
List the top 10 companies with the most new granted patents for 2019.
Calculation
````{r eval=FALSE}

most_patents_US_2019 <- combined_patent_data[type.x == 2 & lubridate::year(date) == "2019", .N, by = organization ]
most_patents_US_2019[order(-N)] %>%
  slice(1:10) %>%
  write_rds("02_data_wrangling/most_patents_US_2019.rds")

````
Result
````{r}
most_patents_US_2019 <- read_rds("patents_data/most_patents_US_2019.rds")
most_patents_US_2019

````


## 4.3 What is the most innovative tech sector?
For the top 10 companies (worldwide) with the most patents, 
what are the top 5 USPTO tech main classes?

Calculation
````{r calculation, eval=FALSE}
top_tech_main_classes <- combined_uspc_data[type.x == 2 | type.x == 3, .N, by = mainclass_id]
top_tech_main_classes[order(-N)] %>%
  slice(1:5) %>%
  write_rds("02_data_wrangling/top_tech_main_classes.rds")
````
Result
````{r}
top_tech_main_classes <- read_rds("patents_data/top_tech_main_classes.rds")
top_tech_main_classes

````














