---
title: "My Journal "
author: "Frederick Blome"
date: "2020-11-24"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

Last compiled: `r Sys.Date()`

# Challenge 1 - Intro to tidyverse

Last compiled: `r Sys.Date()`

First do some Loading and joining Data

````{r}
# SALES ANALYSIS ----

# 1.0 Load libraries ----

library(tidyverse)
library(readxl)

# 2.0 Importing Files ----

bikes_tbl <- read_excel(path = "./bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel(path = "./bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl <- read_excel(path = "./bike_sales/01_raw_data/bikeshops.xlsx")

# 3.0 Examining Data ----

# 4.0 Joining Data ----

bike_orderlines_joined_tbl <- orderlines_tbl %>% left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))
````
## Wrangling of Data

Next we do some wrangling of the Data
````{r}
# 5.0 Wrangling Data ----
# All actions are chained with the pipe already. You can perform each step separately
# and use glimpse() or View() to validate your code. Store the result in a variable at the end of the steps.

bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  
  # 5.1 Separate category name
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ", ") %>%
  
  # 5.2 Add the total price (price * quantity) 
  # Add a column to a tibble that uses a formula-style calculation of other columns
  mutate(total.price = price * quantity) %>%
  
  # 5.3 Optional: Reorganize. Using select to grab or remove unnecessary columns
  # 5.3.1 by exact column name
  select(-...1, -gender) %>%
  
  # 5.3.2 by a pattern
  # You can use the select_helpers to define patterns. 
  # Type ?ends_with and click on Select helpers in the documentation
  select(-ends_with(".id")) %>% 
  
  # 5.3.3 Actually we need the column "order.id". Let's bind it back to the data
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 

  # 5.3.4 You can reorder the data by selecting the columns in your desired order.
  # You can use select_helpers like contains() or everything()
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>% 
  
  # 5.4 Rename columns because we actually wanted underscores instead of the dots
  # (one at the time vs. multiple at once)
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))
````

## Analysis of sales by location

Get insights and plot Bar Charts

1. Manipulate Data
````{r}

# 6.0 Business Insights ----

# 6.1 Sales by location (state) ----
  
  #Step 1 - Manipulate
  
  sales_by_state_tbl <- bike_orderlines_wrangled_tbl %>%
  
  #Select columns
  select(state, total_price) %>%
  
  #Grouping by state and summarizing sales
  group_by(state) %>%
  summarize(sales = sum(total_price)) %>%
  
  #Format $ Text
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
````
2. Visualize Data
````{r}
  #Step 2 - Visualize
  
  sales_by_state_tbl %>%
    
    # Setup canvas with the columns state (x-axis) and sales (y-axis)
    ggplot(aes(x = state, y = sales)) +
    
    # Geometries
    geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
    geom_label(aes(label = sales_text)) + # Adding labels to the bars
    geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
    
    # Formatting
    # scale_y_continuous(labels = scales::dollar) + # Change the y-axis. 
    # Again, we have to adjust it for euro values
    scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                      decimal.mark = ",", 
                                                      prefix = "", 
                                                      suffix = " €")) +
    #Theme
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    
    
    labs(
      title    = "Revenue by state",
      subtitle = "Upward Trend",
      x = "", # Override defaults for x and y
      y = "Revenue"
    )
  

````

## Sales by location and year

Get insights and plot Bar Charts
1. Manipulate Data
````{r}
# 6.2 Sales by Location (state) and year ----
  
  library(lubridate)

  # Step 1 - Manipulate

  sales_by_year_state_tbl <- bike_orderlines_wrangled_tbl %>%
    
    # Select columns and add a year
    select(order_date, total_price, state) %>%
    mutate(year = year(order_date)) %>%
    
    
    # Group by and summarize year and state
    group_by(year, state) %>% 
    summarize(sales = sum(total_price)) %>%
    ungroup() %>%
    
    #Format $ Text
    mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                       decimal.mark = ",", 
                                       prefix = "", 
                                       suffix = " €"))
````
2. Visualize Data
````{r}

# Step 2 - Visualize
  
  sales_by_year_state_tbl %>%
    
    #Set up x, y, fill
    ggplot(aes(x = year, y = sales, fill = state)) +
    
    #Geometries
    geom_col() +  # Use geom_col for a bar plot
    geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
    
    #Facet
    facet_wrap(~ state) +
  
    #Formatting
    scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                      decimal.mark = ",", 
                                                      prefix = "", 
                                                      suffix = " €")) +
    #Theme
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +

    labs(
      title = "Revenue by year and state",
      subtitle = "Nearly each state has an upward trend",
      fill = "state", # Changes the legend name
      x = "",
      y = "Revenue"
    )

````




















# Challenge 2 - Web scraping

## Get Data via an API
Get Data from first Pokemon Bulbasaur
Set eval=FALSE because Dataset is very very large
````{r eval=FALSE}
#Acces to a Database using HTTP and API ----

#Import library
library(tidyverse)
library(glue)
library(httr)
library(jsonlite)

# First http request to Pokemon API
resp <- GET("https://pokeapi.co/api/v2/pokemon/1")
resp


#Convert raw Unicode into a character vector in JSON format
resp %>% 
  .$content %>% 
  rawToChar() %>% 
  fromJSON()


````

## Scrape Data from website

````{r}
## Create a small database of at least one category
## database content: model names and price for at least one category
library(tidyverse)
library(glue)
library(rvest)
library(xopen)
library(jsonlite)
library(stringi)

#Set URL to specific website
url_racingbike <- "https://www.rosebikes.de/fahrr%C3%A4der/rennrad"
````
### Open url
````{r eval=FALSE}
# Open the URL in webbrowser
xopen(url_racingbike)
````

### Read in the HTML
````{r}
# Read in the HTML for the Racingbike URL
html_racingbike <- read_html(url_racingbike)

# Web scrape the ids for the racingbike
name <- html_racingbike %>%
                  html_nodes(css = ".catalog-category-bikes__title") %>%
                  html_text() %>%
                  #stringr::str_extract_all("[A-Z]+(?=\\n)") %>%
                  tibble()
name

prices <- html_racingbike %>%
                  html_nodes(css = ".catalog-category-bikes__price-title") %>%
                  html_text() %>%
                  tibble()
prices
````

### Merge the two tibbles
````{r}
# Merge the two tibbles together
combo <- bind_cols(name,prices)

combo

````






# Challenge 3 - Data wrangling

## Libraries
````{r eval=FALSE}
# Tidyverse
library(tidyverse)
library(vroom)

# Data Table
library(data.table)

````

## Data Import
````{r eval = FALSE}
# 2.1 Assignee  Data ----
col_types_ass <- list(
  id = col_character(),
  type = col_integer(),
  name_first = col_skip(NULL),
  name_last = col_skip(NULL),
  organization = col_character()
)

assignee_tbl <- vroom(
  file       = "00_data/patents_data/assignee.tsv", 
  delim      = "\t", 
  col_types  = col_types_ass,
  na         = c("", "NA", "NULL")
)


#2.2 Patents assignee data ----

col_types_pat_ass <- list(
  patent_id = col_character(),
  assignee_id = col_character(),
  location_id = col_skip()
)

patent_assignee_tbl <- vroom(
  file        = "00_data/patents_data/patent_assignee.tsv",
  delim       = "\t",
  col_types   = col_types_pat_ass,
  na          = c("", "NA", "NULL")
)

#2.3 Patents data ----

col_types_pat <- list(
  id = col_character(),
  type = col_character(),
  number = col_skip(),
  country = col_skip(),
  date = col_date("%Y-%m-%d"),
  abstract = col_skip(),
  title = col_skip(),
  kind = col_skip(),
  num_claims = col_skip(),
  filename = col_skip(),
  withdrawn = col_skip()
)

patents_tbl <- vroom(
  file        = "00_data/patents_data/patent.tsv",
  delim       = "\t",
  col_types   = col_types_pat,
  na          = c("", "NA", "NULL")
)


# 2.4 USPC data ----

col_types_uspc <- list(
  uuid = col_skip(),
  patent_id = col_character(),
  mainclass_id = col_character(),
  subclass_id = col_skip(),
  sequence = col_skip()
)

uspc_tbl <- vroom(
  file        = "00_data/patents_data/uspc.tsv",
  delim       = "\t",
  col_types   = col_types_uspc,
  na          = c("", "NA", "NULL")
)

````

## Merge data
````{r eval = FALSE}
# Convert to data.table ----

setDT(assignee_tbl)
setDT(patent_assignee_tbl)
setDT(patents_tbl)
setDT(uspc_tbl)

#Merge assignee and patent_assignee by assignee_id
combined_assignee_data <- merge(x = assignee_tbl, y = patent_assignee_tbl,
                                by.x    = "id",
                                by.y    = "assignee_id", 
                                all.x = FALSE,
                                all.y = TRUE)

# Merge combined_assignee_data with patents_tbl
combined_patent_data <- merge(x = combined_assignee_data, y = patents_tbl,
                              by.x      = "patent_id",
                              by.y      = "id",
                              all.x = FALSE,
                              all.y = TRUE)

# Merge combined_patent_data with uspc_tbl
combined_uspc_data <- merge(x = combined_patent_data, y = uspc_tbl,
                            by.x        = "patent_id",
                            by.y        = "patent_id",
                            all.x = FALSE,
                            all.y = TRUE)


````

## Analysis of Data

### What US company / corporation has the most patents?
List the 10 US companies with the most assigned/granted patents.
Calculation
````{r eval=FALSE}
most_patents_US <- combined_assignee_data[type == 2, .N, by = organization] # 2- US company or Corporation
most_patents_US[order(-N)]  %>% # order in descending way and slice only first 10 entries
    slice(1:10) %>%
  write_rds("02_data_wrangling/most_patents_US.rds")
````
Result
````{r}
most_patents_US <- read_rds("patents_data/most_patents_US.rds")
most_patents_US
````

### What US company had the most patents granted in 2019?
List the top 10 companies with the most new granted patents for 2019.
Calculation
````{r eval=FALSE}

most_patents_US_2019 <- combined_patent_data[type.x == 2 & lubridate::year(date) == "2019", .N, by = organization ]
most_patents_US_2019[order(-N)] %>%
  slice(1:10) %>%
  write_rds("02_data_wrangling/most_patents_US_2019.rds")

````
Result
````{r}
most_patents_US_2019 <- read_rds("patents_data/most_patents_US_2019.rds")
most_patents_US_2019

````


### What is the most innovative tech sector?
For the top 10 companies (worldwide) with the most patents, 
what are the top 5 USPTO tech main classes?

Calculation
````{r calculation, eval=FALSE}
top_tech_main_classes <- combined_uspc_data[type.x == 2 | type.x == 3, .N, by = mainclass_id]
top_tech_main_classes[order(-N)] %>%
  slice(1:5) %>%
  write_rds("02_data_wrangling/top_tech_main_classes.rds")
````
Result
````{r}
top_tech_main_classes <- read_rds("patents_data/top_tech_main_classes.rds")
top_tech_main_classes

````































# Challenge 4 - Data Visualization

## Libraries
````{r}
library(tidyverse)
library(lubridate)
````

## Data Import
````{r}
covid_data_tbl <- read_csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")
````

## Data wrangling part 1
````{r}
cum_cases_tbl <- covid_data_tbl %>%
  mutate(date = lubridate::dmy(dateRep)) %>% 
    
  # Filter for cases in 2020
  filter(year == 2020) %>%
  
  # Select relevant columns
  select(cases, countriesAndTerritories, date, month) %>%


  filter(countriesAndTerritories == "United_States_of_America" |
         countriesAndTerritories == "Germany" |
         countriesAndTerritories == "France" |
         countriesAndTerritories == "Spain" |
         countriesAndTerritories =="United_Kingdom") %>%
  arrange(date) %>%
  
  # Group and calculate cumulative cases each for country
  group_by(countriesAndTerritories) %>%
  mutate(cum_cases = cumsum(cases))
  
  # get list with cummulative cases per region
  max_cum_cases_tbl <- cum_cases_tbl %>%
    mutate(day = day(date)) %>%
    group_by(countriesAndTerritories) %>%
    mutate(max_cases = max(cum_cases)) %>%
    filter(month == month(today()) & day == day(today())) %>%
    select(countriesAndTerritories, max_cases, date) %>%
    
    #only labels for German and USA
    filter(countriesAndTerritories == "United_States_of_America" | 
             countriesAndTerritories == "Germany")
  
````    
    
## Data visualization part 1

````{r fig.width=12, fig.height=9}
cum_cases_tbl %>%
  ggplot() +
  
  geom_line(aes(x = date, y = cum_cases, color = countriesAndTerritories),
            size = 1.5) +
    
  theme_dark() +
    
  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 1
    ),
    plot.title = element_text(face = "bold"),
    plot.caption = element_text(face = "bold.italic"),
    legend.title = element_text(face = "bold"),
    legend.position = "bottom"
  ) +
    
  expand_limits(y = 1.5e7) +
    
  scale_y_continuous(labels = scales::dollar_format(scale = 1e-6,
                                                    prefix = "",
                                                    suffix = "M")) +
  scale_x_date(date_labels = "%B", date_breaks = "1 month") +
  
  labs(
      title = "COVID-19 confirmed cases worldwide",
      subtitle = str_glue("Date: {today()}"),
      x = "Year 2020",
      y = "Cumulative Cases",
      caption = "Labels for USA and Germany"
    ) +
  

    
    
  geom_label(aes(x = date, y = max_cases, label = max_cases),
             vjust = 1.8,
             hjust = 0.8,
             data = max_cum_cases_tbl,
             size = 5,
             fill = "#ba9538",
             color = "white")
              

  
````
I don't know wh my labels are not shown! When I build the website with the code in the journal.Rmd file the plot is visible with the labels like intended. But when I build the website with "Build Website" or with source("build_website.R") there are no labels!!!

## Data wrangling part 2
````{r}
library(maps)
  world <- map_data("world")
  
  
  mortality_tbl <- covid_data_tbl %>%
    
    # calculate overall deaths
    group_by(countriesAndTerritories) %>%
    mutate(cum_deaths = sum(deaths)) %>%
    # Calculate mortality rate
    summarise(cum_deaths, mortality_rate = cum_deaths / popData2019 * 100) %>%
    ungroup() %>%
    
    #issue with different naming
    mutate(across(countriesAndTerritories, str_replace_all, "_", " ")) %>%
    mutate(countriesAndTerritories = case_when(
      
      countriesAndTerritories == "United Kingdom" ~ "UK",
      countriesAndTerritories == "United States of America" ~ "USA",
      countriesAndTerritories == "Czechia" ~ "Czech Republic",
      TRUE ~ countriesAndTerritories
    )) %>%
    
    
    left_join(world, by = c("countriesAndTerritories" = "region"), copy = FALSE) %>%
      select(mortality_rate, countriesAndTerritories, long, lat)
  


      sum_deaths <- covid_data_tbl %>%
      summarize(cum_deaths = sum(deaths))
      
      num_deaths = sum_deaths[[1]]

````

## Data Visualization part 2

````{r}
# Visualization part 2 ----

  world_map_plot <- mortality_tbl %>%
    
    ggplot() +
    
    geom_map(aes(x = long,
                 y = lat,
                 map_id = countriesAndTerritories,
                 fill = mortality_rate),
             map = world) +
    
    theme_dark() +
    theme(plot.title = element_text(face = "bold"),
          plot.caption = element_text(face = "bold.italic"),
          legend.title = element_text(face = "bold"),
          legend.position = "right") +
    
    scale_fill_gradient(low = "red", 
                        high = "black",
                        name = "Mortality Rate in Percent") +
    
    labs(
      title = "Confirmed COVID-19 deaths relative to the size of the population",
      subtitle = str_glue("More than {num_deaths} Deaths confirmed COVID-19 deaths worldwide"),
      caption = str_glue("Date: {now()}")

    ) 

      world_map_plot    

````


